Evaluating approaches to deriving photometric redshift posterior probability distribution functions for \textsc{LSST}

### 2019-03-10 paper/tex/methods.tex
moved LePhare because it has no info beyond the intro

We test three publicly available and commonly used template-based codes, \bpz, \eazy, and \lephare, that share the standard physically motivated approach of calculating model fluxes for a set of template SEDs on a grid of redshift values and evaluating a merit function using the observed and model fluxes.
These three also share the \chisq\ merit function
\begin{equation}
	\label{eq_temp_chi}
	\chi^{2}(z, T, A) \equiv \sum_{b}^{N_{\rm{filt}}} \left(\frac{F^{\rm{obs}}_{b} - A F^{\rm{mod}}_{b}(T, z)}{\sigma^{\rm{obs}}_{b}}\right)^{2},
\end{equation}
of normalization factor $A$, template $T$, and redshift $z$, which is a sum of observed flux error $\sigma_{b}^{\rm{obs}}$-weighted squared differences between the observed flux $F^{\rm{obs}}_{b}$ and the normalized predicted flux $F^{\rm{mod}}_{b}(T, z)$ in $N_{\rm{filt}}$ photometric filters $b$, which in our case is the \lsst\ $ugrizy$ filters.

@@

\bpz\footnote{\url{http://www.stsci.edu/~dcoe/BPZ/}} \citep[Bayesian Photometric Redshift,][]{Benitez:00} is a template-based \pz\ code that determines the likelihood $p(C \mid z, T)$ of a galaxy's observed colours $C$ for a set of SED templates $T$ at redshifts $z$.
The \bpz\ likelihood is related to Equation~\ref{eq_temp_chi} by $p(C \mid z, T) \propto \exp[- \chi^{2} / 2]$.
Given a Bayesian prior $p(z, T \mid m_{0})$ over apparent magnitude $m_0$ and assuming that the SED templates are spanning and exclusive, \bpz\ constructs the redshift posterior $p(z \mid C, m_0)$ by marginalizing over all SED templates as in \citep[Eq.~3 from][]{Benitez:00}, corresponding to setting the parameter \texttt{PROBS\_LITE=TRUE} in the \bpz\ parameter file.
The \bpz\ prior is the product of an SED template proportion that varies with apparent magnitude $p(T \mid m_{0})$ and a prior $p(z \mid T, m_{0})$ over the expected redshift as a function of apparent magnitude and SED template.

@@

\eazy\footnote{\url{https://github.com/gbrammer/eazy-photoz}} \citep[Easy and Accurate Photometric Redshifts from Yale,][]{Brammer:08} extends the basic \chisq\ fit procedure that defines template-fitting approaches.
The algorithm models the observed photometry with a linear combination of template SEDs at each redshift.
The best-fit SED is found by simultaneously fitting one, two, or all of the templates via \chisq\ minimization, which is distinct from marginalizing across all templates.
The minimized \chisq\ likelihood at each redshift is then combined with an apparent magnitude prior to obtain the redshift posterior PDF.
We note that the utilization of the best-fit SED rather than a proper marginalization does not lead to the correct posterior distribution, an implementation issue that has now been identified and will be addressed by the developers in the future.
\eazy\ can account for uncertainty in the template set by adding in quadrature to the flux errors an empirically derived template error as a function of redshift.

@@

\textsc{LePhare}\footnote{\url{http://www.cfht.hawaii.edu/~arnouts/lephare.html}}\citep[Photometric Analysis for Redshift Estimate,][]{Arnouts:99,Ilbert:06} is a photo-$z$ reconstruction code based on a $\chi^2$ template-fitting procedure.
The observed colors are matched with the colours predicted from a set of spectral energy distribution (SED) which can be either synthetic or based on a semi-empirical approach. %\textsc{LePhare} has been used to produce the COSMOS2015 photo-$z$ catalogue \citep{Laigle:16}.

Each SED is convolved with the simulated LSST filter transmission curves (accounting for instrument efficiency).
The computed photo-$z$ is then the value that minimizes the merit function $\chi^2 (z,T,A)$ from \citet[]{Arnouts:99}, and given in Equation~\ref{eq_temp_chi}.

In this paper we use \textsc{LePhare v 2.2}.
The set of templates used for fitting the photo-$z$'s are the 100 discrete Buzzard SED templates as described in section~\ref{sec:buzztemplates}, and the full $p(z)$ corresponds to the likelihoods calculated at each point on our $z$-grid.

>>>>

We test three publicly available and commonly used template-based codes, \lephare, \bpz, and \eazy, that share the standard physically motivated approach of calculating model fluxes for a set of template SEDs on a grid of redshift values and evaluating a merit function using the observed and model fluxes.
These three also share the \chisq\ merit function
\begin{equation}
	\label{eq_temp_chi}
	\chi^{2}(z, T, A) \equiv \sum_{b}^{N_{\rm{filt}}} \left(\frac{F^{\rm{obs}}_{b} - A F^{\rm{mod}}_{b}(T, z)}{\sigma^{\rm{obs}}_{b}}\right)^{2},
\end{equation}
of normalization factor $A$, template $T$, and redshift $z$, which is a sum of observed flux error $\sigma_{b}^{\rm{obs}}$-weighted squared differences between the observed flux $F^{\rm{obs}}_{b}$ and the normalized predicted flux $F^{\rm{mod}}_{b}(T, z)$ in $N_{\rm{filt}}$ photometric filters $b$, which in our case is the \lsst\ $ugrizy$ filters.

\lephare \footnote{\url{http://www.cfht.hawaii.edu/~arnouts/lephare.html}}\citep[Photometric Analysis for Redshift Estimate,][]{Arnouts:99,Ilbert:06} matches observed colors with those predicted from a template set, which can be semi-empirical or entirely synthetic, directly according to Equation~\ref{eq_temp_chi} without modification.
The reported \pzpdf\ is an arbitrary normalization of the likelihood evaluated on the output redshift grid.
%\textsc{LePhare} has been used to produce the COSMOS2015 photo-$z$ catalogue \citep{Laigle:16}.
Here we use \lephare-v 2.2 with the DC1 template set of Section~\ref{sec:buzztemplates}.

@@

\bpz \footnote{\url{http://www.stsci.edu/~dcoe/BPZ/}} \citep[Bayesian Photometric Redshift,][]{Benitez:00} determines the likelihood $p(C \mid z, T)$ of a galaxy's observed colours $C$ for a set of SED templates $T$ at redshifts $z$.
The \bpz\ likelihood is related to Equation~\ref{eq_temp_chi} by $p(C \mid z, T) \propto \exp[- \chi^{2} / 2]$.
Given a Bayesian prior $p(z, T \mid m_{0})$ over apparent magnitude $m_0$ and assuming that the SED templates are spanning and exclusive, \bpz\ constructs the redshift posterior $p(z \mid C, m_0)$ by marginalizing over all SED templates as in \citep[Eq.~3 from][]{Benitez:00}, corresponding to setting the parameter \texttt{PROBS\_LITE=TRUE} in the \bpz\ parameter file.
The \bpz\ prior is the product of an SED template proportion that varies with apparent magnitude $p(T \mid m_{0})$ and a prior $p(z \mid T, m_{0})$ over the expected redshift as a function of apparent magnitude and SED template.

@@

\eazy \footnote{\url{https://github.com/gbrammer/eazy-photoz}} \citep[Easy and Accurate Photometric Redshifts from Yale,][]{Brammer:08} extends the basic \chisq\ fit procedure that defines template-fitting approaches.
The algorithm models the observed photometry with a linear combination of template SEDs at each redshift.
The best-fit SED is found by simultaneously fitting one, two, or all of the templates via \chisq\ minimization, which is distinct from marginalizing across all templates.
The minimized \chisq\ likelihood at each redshift is then combined with an apparent magnitude prior to obtain the redshift posterior PDF.
We note that the utilization of the best-fit SED rather than a proper marginalization does not lead to the correct posterior distribution, an implementation issue that has now been identified and will be addressed by the developers in the future.
\eazy\ can account for uncertainty in the template set by adding in quadrature to the flux errors an empirically derived template error as a function of redshift.

@@
